\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{hw}
\input{macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{P3}{October 25, 2006}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Assignment 3: Fundamental Concepts}

{\em This assignment is due on} {\bf Friday, November 6, 2006 at 11:59
  p.m.}  We appreciate creativity, but please do not invent your own
  deadlines.  


\section{Purpose of this Assignment}

The purpose of this assignment is to help you think about both the
current state of the art in your particular research field, as well as
the major lasting intellectual contributions to your field.  

Revisiting lasting research contributions is a useful exercise that is
performed in many disciplines.  See, for example, the ``Recommended
Reading'' column that appears in ACM's {\em Computer Communication
  Review}:  \url{http://www.sigcomm.org/ccr/drupal/?q=node/61}.

In addition to helping you think about the ``big ideas'' from your area,
this assignment is also designed to help you develop your teaching
skills; you may be asked at many points in your career to summarize the
contributions of your field.

This will also prepare you for the next assignment (helpful hint: PS~4
will, in some ways, be an analog to PS~2).

\section{Your Task}

Your task is to create a ``high level'' syllabus for a first-year
Ph.D. course in your research area.  (By ``high level'', we want you to
focus on identifying themes that you would want to teach from your area,
rather than doing mundane things like designing assignments, tests,
etc.).  Your syllabus should be organized roughly as follows:

\begin{enumerate}
\item 4-5 fundamental concepts from your area.  You should provide a 2-3
  sentence summary describing each concept.
\item for each concept, 2-4 ``lectures'' which represent important
  sub-topics or details related to that area.  (One sentence per
  detailed idea is fine.)
\item 2 big open problems from the area. Two-sentences per problem is
  sufficient. 
\end{enumerate}

{\bf An outline is sufficient.  Making lectures is not required!}

To help you get started: From networking, a fundamental concept could be
``tree building'' and might include a lecture on Internet routing.  From
machine learning, a fundamental concept could be ``generalization'',
which might include a lecture on cross-validation.

In addition to performing the group work for this assignment, every
student should turn in their own syllabus.  The group should then turn
in a merged syllabus reached by consensus.

{\em Note:} This assignment is difficult.  In fact, you will probably
find that most syllabi are not organized in this way because even
experts have a hard time doing this!  Where there is ambiguity, just
make a decision.

{\em There will be no presentation for this assignment.}

\end{document}
