\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{MA2}{October 19, 2009}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Mini-Assignment 3: Project
  Interim Report} 

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Wednesday, October 26, 2009 by 11:59p.m. to
  the TAs.}

\section{Purpose of this Assignment}

The purpose of this assignment is to ensure that you are ``on track'' to
complete a quality {\bf main project}, complete with writeup and
presentation.  We know that the general tendency is to leave everything
until the last minute, so this assignment serves as a checkpoint to make
certain that you are making progress on the project, as well as on the
final writeup.

\section{Task}

Please turn in an {\bf outline} of your final project writeup, complete
with page budgets for each section.  To the extent possible, please take
the approach described in class: work backwards from the paper that you
would like to have.  Don't just provide us a ``skeleton'' with
high-level sections; please include as much detail as you can.  Please
follow the following guidelines for each section:
\begin{itemize}
\itemsep=-1pt
\item The {\em introduction} section should include a
  paragraph-by-paragraph outline of what you plan to write.  To the
  extent that it makes sense, please follow the introduction ``formula''
  that we laid out in the Lecture 12 notes.
\item Your {\em related work} section should be complete.  In other
  words, please turn in a complete draft of this section (with complete
  sentences). 
\item In the {\em evaluation} section, you should include a description
  of the charts and graphs you plan to include in the section, as well
  as {\em justification} for why you will include them (i.e., what
  question are they solving?).
\item If you have background, design, setup, or discussion sections, you
  should have at least a start on those sections, too.  Where possible,
  indicate your plans to include specific figures and diagrams.
\end{itemize}
\noindent
This assignment will be graded like every other assignment.  It is for
your benefit, so please take it seriously.  We will note who is waiting
until the last minute.  If you are lost on your term project, please
come see us.

\end{document}
