\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{MA1}{August 23, 2010}{Instructor: Profs. Abowd/Feamster}
{College of Computing, Georgia Tech}{Mini-Assignment 1: Why a Ph.D.?}

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Wednesday, August 25, 2010 by 11:59p.m. to
  the TAs.}

\section{Purpose of this Assignment}

The purpose of this assignment is to encourage you to write down your
current goals for getting a Ph.D.  Putting your thoughts down on paper
will help you think clearly about the ``big picture'' reasons that you
are here.  During the course of graduate school, you may want to revist
these ``macro'' goals to see whether you are making progress towards
achieving them.

\section{Task}

Write a response to the following questions:
\begin{itemize}
\itemsep=-1pt
    \item Why are you doing the Ph.D.? (1-2 paragraphs)
    \item What researchers do you strive to emulate?
    \item What research result(s) do you most admire?
\end{itemize}
\noindent
If this is your first exposure to research, you may have a difficult
time answering the latter questions, but now is a very good time to
start seeking out examples of research (and researchers) that you
value.  This process will begin the process of developing
research ``taste'' which you will continue to refine throughout your
research career.


\end{document}
