\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{PR1}{September 15, 2008}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Mini-Project Assignment}

{\em This assignment has multiple due dates, outlined at the end of this
  document.}

\section{Summary, Purpose, and Parameters}

The purpose of the mini-project is to allow you to explore the breadth
of research that is being performed within the college.  Thus, you may
want to make it a goal of your mini-project to explore an discipline
that is outside of your immediate research interest or area.  This
exploratory process serves several important functions:

\begin{enumerate}
\item It gives you an excuse to approach another faculty member in the
  college who you may not otherwise approach.  You may even find this
  relationship with a faculty member outside of your research area to be
  a useful independent source of advice throughout your graduate career.
\item It introduces you to research outside your immediate area.  This
  breadth of exposure may prove useful in your own research.  For
  example, you may ultimately apply techniques you learn from your
  mini-project area to your own research area at some later point.  Who
  knows: the mini-project may even become your dissertation topic!
\item It allows faculty outside of your area to meet you. You can
  ultimately benefit from impressing a broader range of faculty (think
  career connections, etc.).
\item It's exploratory and fun!  You will ultimately narrow down into a
  very specific research problem and area, and you won't get too many
  chances like this to explore research in other areas.
\end{enumerate}

It is up to you to (1)~select a mini-project advisor, who can help you
define the mini-project; (2)~define the mini-project; (3)~complete the
mini-project to the satisfaction of the mini-project advisor (and us).
The specific milestones for the project, and specification of those
milestones, is included below.

The scope of the project should be something that you can complete in
5-6 weeks as a ``side project'' (keeping in mind that most of your work
will be on your main project).

We encourage you to do more than one mini-project!  In terms of grading
criteria below, if you do more than one mini-project, we will use the
highest mini-project grade from all of your mini-projects as your
overall mini-project grade.

\section{Milestones and Important Dates}

You can start your mini-project anytime, as long as you complete it by
December 7.   You must provide a title for your mini-project and the
name of the faculty member with whom you are working by the due date
below.

\begin{center}
\begin{tabular}{lrp{3.5in}}
{\bf Date} & {\bf \% of Grade} & {\bf Milestones} \\ \hline
September 29 & 5\% & Title and faculty member \\
December 5 & 25\% & Final mini-project report \\
December 5 & 70\% & Faculty evaluation
\end{tabular}
\end{center}

Grading for this project will be A, B, or F.  In addition to the initial
report of who you are working with and the topic you have chosen, your
final mini-project grade will have two components:

\begin{enumerate}
\itemsep=-1pt
\item We will ask the mini-project advisor for a grade (A or F) for the
  project and a {\bf brief evaluation/summary of your work}. This
  component will form 70\% of your mini-project grade.  Your
  mini-project advisor will email this to the TAs. {\em It is your
  responsibility to tell the mini-project advisor the email addresses of
  the TAs, and the due date for this evaluation.}
%
\item Your {\bf final mini-project report} is a one-page summary of the
  mini-project: (1)~the problem/topic, (2)~what you did, and (3)~what
  you learned from the project.  This component of the project will also
  have an A or F component. This component will form 25\% of your
  mini-project grade.
\end{enumerate}

\end{document}
