\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{MA4}{November 21, 2007}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Mini-Assignment 4: Multi-Resolution
Elevator Pitch}

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Wednesday, November 28, 2007 by 11:59p.m.}

\section{Purpose of this Assignment}


When you attend conferences, visit other universities, and generally
interact with your other research colleagues, they will almost
unfailingly ask you ``So what are you working on?'' or some variant of
this question.  {\em You must offer a coherent response.}  In many
cases, this will the your colleague's primary mode for judging you and
your research.  A strong, clear answer to this question can form a very
strong impression; on the flip side, a flaky response can be a
``career-limiting'' move.

The coherent response is commonly known as an ``elevator pitch''.  Your
elevator pitch should be multi-resolution: you should have a research
summary that gives the main idea of your work in no more than 30 seconds
(the length of an elevator ride, the time you might cross paths with
someone in the restroom/hallway, etc.).  Your short elevator pitch is
also very useful for explaining to people outside of your immediate area
(often helpful for broader PR).  If a colleague engages you in further
discussion, you should be prepared to gently dive into more details (a
5-minute elevator pitch...a ``cab ride pitch'').

\section{Task}


Your task is to devise a multi-resolution elevator pitch.  The written
portion of this assignment has two parts:
\begin{itemize}
\item A 100-word summary of what you are currently working on.  This
  summary could be a high-level summary of one particular problem you
  are working on or, if you are working on multiple projects, a
  high-level description of the general types of problems that you are
  interested in.
\item A similar 1000-word summary.
\end{itemize}
\noindent
You will present your 30-second elevator pitch to the class during
lecture.  {\em The 30-second time limit will be strictly enforced with
an air horn and [cherry] tomatoes!}

The next assignment, your research presentation, is effectively a third,
longer elevator pitch.


\end{document}
