\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{hw}
\input{macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{P1}{September 15, 2006}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Assignment 2: Cross-Pollination}

{\em Complete this assignment with your assigned research group.  This
  assignment is due on} {\bf Friday, October 2, 2006.}

\section{Purpose of this Assignment}

The purpose of this assignment is to encourage {\em cross-pollination}
of ideas across research areas.  Many great research ideas involve
applying concepts or techniques from one area to another.  This
assignment will help you both learn about research in other areas and
experiment with combining ideas from your research area with those from
other areas to come up with new ideas.


\section{Your Task}

For each of the two research papers you selected in the first
assignment, you should find a paper from another research area and come
up with a possible research topic that involves the combination of the
ideas from the two research areas.  Each paper must be matched with a
different research area.  

This assignment involves the following two tasks:

\begin{enumerate}
\itemsep=-1pt
\item Compose a research proposal for each of the two new ideas.  Your
research proposal should be a 1-page description of the problem that
answers the following questions: (1)~why the problem you are proposing
to solve is important; (2)~Why the combination of the two ideas makes
sense; and (3)~How you might go about solving the problem you propose.
\item Prepare a talk on one of your ideas that address the questions
  above.
\end{enumerate}


\end{document}
