\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{A2}{September 29, 2008}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Assignment 2: Cross-Pollination}

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Monday, October 6, 2008 by 11:59p.m. to
  the TAs.}

\section{Purpose of this Assignment}


The purpose of this assignment is to encourage {\em cross-pollination}
of ideas across research areas.  Many great research ideas involve
applying concepts or techniques from one area to another.  This
assignment will help you both learn about research in other areas and
experiment with combining ideas from your research area with those from
other areas to come up with new ideas.

\section{Problem}

For each of the two research papers you selected in the first
assignment, you should find a paper from another research area and come
up with a possible research topic that involves the combination of the
ideas from the two research areas.  Each paper must be matched with a
different research area.

\section{Task}

\begin{enumerate}
\itemsep=-1pt
\item {\em Read others' papers/summaries from Assignment \#1.} These
  papers are all posted at:\\ \url{http://swiki.cc.gatech.edu/cs7001/43}.
  We have asked the TA to post your own summaries of these papers, too,
  to save you all some reading.  This should happen shortly, but, until
  then, please consider using our time-saving techniques from Lecture 4.
%
\item {\em Compose a research proposal for each of the two new ideas.}  Your
research proposal should be a 1-page description of the problem that
answers the following questions: (1)~why the problem you are proposing
to solve is important; (2)~Why the combination of the two ideas makes
sense; and (3)~How you might go about solving the problem you propose.
\end{enumerate}


\end{document}
