\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{MA4}{November 24, 2008}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Mini-Assignment 3: Personal Web Page}

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Monday, December 1, 2008 by 11:59p.m.}

\section{Purpose of this Assignment}


Your job as a researcher is not only to come up with groundbreaking
research results, but also to {\em market} these results to a broader
audience.  Research results that cannot be understood or applied by
others are effectively useless.  The audience you target may vary
depending on the nature of your research (and the nature of your
results), but can include parties such as other researchers in your
field, people working on similar problems in industry, other colleagues
at your university, news outlets, etc.

One of the first places that all of these parties may go to learn about
your research is your personal Web page; therefore, it is important to
have one!  In this assignment, you will construct and publish a personal
research Web page that summarizes your research interests, expertise,
projects, and papers (if you have any of the above). 



For one of the two research papers you selected in the first
assignment, you should find a paper from another research area and come
up with a possible research topic that involves the combination of the
ideas from the two research areas.  Each paper must be matched with a
different research area.


\section{Task}


Construct a personal research Web page with the following components:
\begin{itemize}
\item Your name
\item Your photo
\item Your contact information (office location, phone number, etc.)
\item A short summary of your research interests
\item A section with links to papers and talks
\end{itemize}

{\bf The last slide of your mini-conference presentation should contain
  a link to your home page.}

\noindent
{\em Note:} Try to make the page somehwat aesthetically pleasing.
There's no need for fancy colors, animations, flash, etc.; simple and
readable is good.  The goal should be a professional-looking page that
efficiently transfers the ``high-order bits'' of information.  For many
colleagues, your Web page will be their first (and maybe only!)
impression of you.

\end{document}
