\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{PR1}{September 10, 2007}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Main Project Assignment}

{\em This assignment has multiple due dates, outlined at the end of this
  document.}

\section{Summary, Purpose, and Parameters}

The purpose of this assignment is to give you a first experience in
performing an in-depth research project.  Upon completing this project,
you will have experience in performing all of the elements of a
research project, including:
\begin{itemize}
\itemsep=-1pt
\item managing student-advisor interactions
\item generating research ideas
\item seeing a project through from start to finish
\item giving a research presentation
\item paper writing
\end{itemize}
\noindent
We recommend that you work with your GRA advisor on your main project:
for one, it saves time because the research itself will be performed
outside of this class.  However, don't feel as though this is a hard
constraint if it is inconvenient for you: you are welcome to work with
any faculty member who is willing to advise you on research for the
term.

The rest of this document summarizes the milestones for the project and
their due dates.

%* Who can you work with?
%- We recommend your GRA advisor (saves time, advisor paying for you)
%* When is it due?
%- See calendar (presentation + paper deadlines are there)

%% * How long does the writeup need to be?
%% - As long as it needs to be.  6-10 pages, using the format of your
%%    main conference.  Think of this as a mini-conference paper.
%% - Paper must have proper formatting.
% * The main project can correspond with an 8903.


\section{Milestones}

The {\bf initial report} should indicate (1)~the title of the project and
(2)~the name of the faculty member with whom you are working.

The {\bf interim report} should include:
\begin{enumerate}
\item A one-paragraph {\em problem statement}: why is the problem
  interesting, important, and challenging?
\item A {\em summary} of (a)~what you have accomplished so far, (b)~what
  remains to be done on the project, (c)~any obstacles you foresee in
  accomplishing the remaining tasks.
\item You should include a {\em draft of the related work section} of
  your paper.  This literature survey should be one full page and have
  at least fifteen references.
\end{enumerate}

The {\bf presentation slides} should correspond to the 15-minute talk
you will present at the mini-conference at the end of the term.  Your
talk should have all of the components of a good talk, which we will
cover in class on October 15.  The grading of this part of the project
(the talk {\em and} the slides themselves) will be based on your
adherence to the principles that we describe in this lecture.

The {\bf final project writeup} should be a 6-10 page writeup that
summarizes the work you have completed for your main project.  The
writeup should be formatted in the accepted conference format for your
main conference.  Think of your writeup as a ``mini-conference paper''
that might eventually form the basis of an eventual conference paper
submission.  This writeup should have all of the components of an actual
conference paper, which we will cover in class on October 12.  The
writeup will be graded based on your adherence to the criteria for
writing a good research paper, which we will present in this lecture.

\section{Important Dates and Grading}

All milestones are due by 11:59p.m. by email to the TAs.  No exceptions!
The quality of each of these components of the project will collectively
determine your overall project grade.

\begin{center}
\begin{tabular}{lrp{3.5in}}
{\bf Date} & {\bf \% of Grade} & {\bf Milestones} \\ \hline
September 21 & 5\% & Initial report \\
October 19 & 10\% & Interim report \\
November 19 & 40\% & Presentations slides due to TAs \\
December 7 & 45\% & Final report 
\end{tabular}
\end{center}

\end{document}
