\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{hw}
\input{macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{P1}{August 24, 2006}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Assignment 1: Identifying Good Ideas}

{\em Complete this assignment with your assigned research group.  This
  assignment is due on} {\bf Friday, September 8, 2006.}

\section{Purpose of this Assignment}

This assignment is the first in a series of assignments where you will
take the steps needed to do great research.  In this assignment, you
will perform one of the most common tasks that researchers perform to
find a research problem: you will read the most recent proceedings from
the top conference in your area, select two papers that you think
represent ``good research'', and defend your selections.

What is good research?  This is a central issue that we will explore
over the course of the semester.  As a working definition, the research
should be something that you think will withstand the ``test of time'':
looking back 10 years from now, people should be able to say that the
ideas in the papers you select advanced the field.

\section{Your Task}

{\bf Read conference proceedings.}  Each research group should select
two papers from their respective conference proceedings that represent
``good research''.  Group assignments and respective conference
proceedings are available at: \\
\url{http://www.cc.gatech.edu/classes/AY2007/cs7001_fall/psets/groups.txt}.

{\bf Present a summary to the class.}  Present a 3-minute summary to the
class briefly summarizing the two papers you selected and why you
selected them.  Your three-minute presentation should have two slides,
one slide for each idea.  Each slide should contain a brief summary of
the paper.  Each group should select one person to present the summary.

{\em Note:} The presentation will give you some experience with presentation,
and will also provide the necessary ``advertisement'' for
Assignment~2.

{\bf Turn in a short writeup defending your paper selections.}  Write
one paragraph per selected paper that defends your paper selections.

\end{document}
