\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{A4}{November 23, 2009}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Assignment 4: Talk Reviews}

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Friday, December 4, 2009 at 11:59pm.}

\section{Task}

Your assignment is to review at least four talks {\em per day} of the
mini-conference.  For each talk, please offer scores and comments for
each talk.

Please send an email to the TA with the information below for each of
eight talks you review.  {\em Please send all eight reviews in a single
  email.}

{\em Please be constructive and encouraging with your criticisms.}  We
intend to pass your feedback on to the speaker.

\section{Review Form}

{\bf Talk Title:} \\
{\bf Speaker:} \\
{\bf Your Name:} \\


{\bf Clarity (0-5): } \\
(For example: Is the problem clear?  Is the contribution clear?
Is the structure clear?)

{\bf Presentation Quality (0-5):} \\ (For example: Did speaker make good
use of slides?  Are the slides well prepared?  Is the delivery clear?)


{\bf Audience Engagement (0-5):} \\ (For example: Is the talk suited to the
background of the audience?  Is the talk exciting?  Does the speaker
show good interaction with the audience?  Does the talk tell a story?)


{\bf Detailed comments:} \\



\end{document}
