\documentclass[11pt]{article}


\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}

\newcounter{listcount}
\newcounter{sublistcount}


\handout{A2}{October 4, 2010}{Instructor: Profs. Feamster/Abowd}
{College of Computing, Georgia Tech}{Assignment 2: Creating an Idea}

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Wednesday, October 20, 2009 by 11:59p.m. to
  T-Square.}

\section{Purpose of this Assignment}
The purpose of this assignment is to encourage cross-pollination of
ideas across research areas.  Many great research ideas involve applying
concepts or techniques from one area to another. This assignment will
help you both learn about research in other areas and experiment with
combining ideas from your research area with those from other areas to
come up with new ideas.

\section{Problem}

You should come up with two possible research topics that involve the
combination of the ideas from the two research areas.  This could be a
pairing of any two ideas from either (1)~the wiki (Assignment~1);
(2)~Any published CoC research papers (you can use the CoC research day
programe for a source of ideas).  Each paper must be matched with a
different research area (the more different, the better).



\section{Task}

\begin{enumerate}
\itemsep=-1pt
\item Read others' papers/summaries from Assignment \#1. These papers
  are all posted in T-Square.
%
\item Look over the list of posters and talks from CoC research day (to
  delve more deeply or broadly, check out faculty and student Web pages).
%
\item Compose a research proposal for each of your two new ideas. Your
  research proposal should be a 1-page description of the problem that
  answers the following questions: (1) why the problem you are proposing
  to solve is important; (2) Why the combination of the two ideas makes
  sense; and (3) How you might go about solving the problem you propose.
\end{enumerate}
\noindent
In the next assignment, your classmates will judge your ideas based on
the three criteria we discussed in class: impact, novelty, and clarity.  The
winner for ``best idea'' will receive a cash prize.


\end{document}
