\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{../templates/hw}
\input{../templates/macros.tex}

\begin{document}


\newcounter{listcount}
\newcounter{sublistcount}


\handout{MA1}{September 16, 2009}{Instructor: Profs. Feamster/Gray}
{College of Computing, Georgia Tech}{Mini-Assignment 2: Time Log}

{\em Complete this assignment individually. \\  This
  assignment is due on} {\bf Wednesday, September 30, 2009 by 11:59p.m. to
  the TAs.}

\section{Purpose of this Assignment}

In this assignment, you will keep a detailed record of how you spend
your time.  Through this exercise, you may discover that you may not be
spending your time exactly as you think you are!

\section{Task}

Keep a detailed ``log'' of how you spend your time over the course of
the week.  Write down, in {\em fifteen-minute intervals}:
\begin{itemize}
\item The nature of the activity (work, recreation, etc.)
\item What exactly you did for that time interval
\end{itemize}

Please be as detailed as possible.  For example, if you spent two hours
working, but if you interrupted your work time for ten minutes to browse
the web, get coffee, etc., try to write these times down, too.  Write
down the time it took to transition between activities.  (Why?  Because
context switches in the middle of work can turn out to be significant
productivity hits!).

We know that this assignment may seem tedious.  On the bright side, you
will only have to do this task for one week; many professionals with
``billable time'' keep a record of how they spend their time down to
10-minute intervals.   

Additionally, keeping a fine-grained record of your time will allow you
to keep track of little wasted time ``slices'' that add up to a
significant amount of time.  Many productive people figure out how to
make the best use of these very small time slices (e.g., reading a
newspaper article while waiting for the train).




\end{document}
